---
title: "Animation and Keyframes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{animation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```

```{r setup}
library(minicss)
library(htmltools)
```


# Introduction

Animation using css consists of

1. A set of *keyframes* describing the appearance at multiple timepoints
2. An *animation* declaration (linked to a particular selector)

## Simple animation in CSS

The following CSS code defines 2 keyframes - the first keyframe defines
the colour as red, and the second keyframe defines the colour as green.  This 
set of keyframes is given the name 'example'.

The `.ugly` class contains the `animation` declaration which says the animation 
should take 1second and should alternate back-and-forth between the two given states
forever (i.e. `infinite` loops)

```
@keyframes example1 {
    from { color: #ff0000; }
    to   { color: #00ff00; }
}

.ugly { animation: example1 1s infinite alternate; }
```


## Create the individual frames with `minicss`

Create a keyframe by initialising an R6 object of class `Keyframe`

```{r}
Keyframe$new(time = 'from', colour = '#000')
```


Create a keyframe by using the `css_keyframe()` function.  

```{r}
css_keyframe(time = 'to', colour = '#00f')
```


Create a keyframe linked to a particular instant in time i.e. 10% through the animation cycle.

```{r}
css_keyframe(time = "10%", color = '#123456')
```


## Modify a keyframe

A `Keyframe` object behaves in the same way as `Style` object, individual declarations
can be updated.

```{r}
kf <- css_keyframe(time = 'to', colour = '#00f')
kf$update(margin = '10px')

kf
```





## Combine individual keyframes into a `Keyframes` object  

### Method 1
```{r}
frame1 <- css_keyframe(time = "from", color = '#123456')
frame2 <- css_keyframe(time = "to"  , color = '#0000ff')

keyframes <- Keyframes$new(name = 'example', frame1, frame2)
keyframes
```


### Method 2

```{r}
keyframes <- Keyframes$new(
  name = 'example',
  css_keyframe(time = "from", color = '#123456'),
  css_keyframe(time = "to"  , color = '#0000ff')
)

keyframes
```

### Method 3

```{r}
keyframes <- Keyframes$new(name = 'example')
keyframes$add(time = "from", color = '#123456')
keyframes$add(time = "to"  , color = '#0000ff')

keyframes
```


## Create an `animation` declaration


This will make use of auto-complete

```{r}
css_prop$animation(name = 'example', duration = 2, iteration_count = 3, direction = 'normal')
```




## Putting it all together


```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Construct individual frames
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
k1 <- css_keyframe('from', color = '#ffffff')
k2 <- css_keyframe('to'  , color = '#123456')
k2$update(css_prop$transform$translateX(40, 'px'))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Combine frames into @keyframes
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
kf <- css_keyframes('ex1', k1, k2)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create style to attach @keyframes to the 'h1' type
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
my_style <- css_style(".swish", font_size = "50px")
my_style$update(
    css_prop$animation('ex1', duration = 1, direction = 'alternate')
)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create a style sheet which includes 
#  - the style for the swish element (including an animation declaration)
#  - the keyframes definition
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
stylesheet <- css_stylesheet(my_style, kf)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create a small HTML snippet which uses this style sheet
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
html <- glue::glue("<html><head>
  <style>{stylesheet}</style>
  </head>
  <body>
  <p class='swish'> Hello #RStats </p>
  </body></html>")
```

```{r echo = FALSE}
html
HTML(html)
```


