---
title: "Properties"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Properties}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```

```{r setup}
library(minicss)
```


# CSS Properties

Property declarations are usually name/value pairs defining the value of a 
particular CSS property e.g. `color: #ff0000`.

Property declarations can be added to styles during intialisation or an update e.g.

```{r}
my_style <- Style$new("h1", color = '#ff0000')
my_style$update(margin = '10px')

my_style
```


Since there are a few hundred different property names, the `css_prop` helper makes
use of auto-complete to help the user write property declarations.

## `css_prop`

```{r}
css_prop$`align-content`$center
```


```{r}
css_prop$margin$auto
```


```{r}
css_prop$color$set('#000')
```







# More complicated properties

The `animation` and `transform` properties are a bit more complex and have
entries in `css_prop` which are a more involved.


## Animation declarations

```{r}
css_prop$animation(name = 'example', duration = 10, timing_function = 'ease', 
                   iteration_count = 'infinite')
```



## Transform declarations

Specialized transform helpers exists for all the standard CSS transforms e.g. translate, 
rotate, skew etc.

```{r}
css_prop$transform$translate(10, 20, unit = '%')
```

