---
title: "Selectors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Selectors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(minicss)
```



# CSS Selectors

Selectors are descriptions of HTML entities on a page.  Combined with a list of property/value pairs, they define which elements a particular style applies to.

Selectors may just be given as a character string, but you can also use the `Selector`
[R6](https://cran.r-project.org/package=R6) class to help build selectors with a
more complex specification.


#### CSS Selectors - Example 1

```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# All things with id = 'greg' with class = 'brady'
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
myselector <- Selector$new()
myselector$class('brady')
myselector$id('greg')

myselector
```


#### CSS Selectors - Example 2

```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# All 'cindy' IDs which are children of 'carol' classes, and 'bobby' IDs which
# are the last child of 'mike' classes
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
parent1 <- css_sel(".carol")$
  parent_of('#cindy')

parent2 <- css_sel()$
  class('mike')$
  attr(job = 'architect')$
  parent_of(
    css_sel()$id('bobby')$pseudo_class(last_child = TRUE)
  )

parent1$and(parent2)

parent1
```