---
title: "Styles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Styles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```

```{r setup}
library(minicss)
library(glue)
```


# Inline styles

A style is a collection of property/value pairs (called declarations).

Use the `prop` helper to auto-complete some common property name/value pairs.

Use the `imp()` function to create an **!important** property.


#### Inline styles - Example 1

```{r}
inline_style <- Style$new(color = 'white', background = '#123456')
inline_style
```

```{r echo = TRUE, eval = FALSE}
glue("<div style = '{inline_style}'>Hello #RStats</div>")
```


```{r echo = FALSE, eval = TRUE}
# Inline styles don't show up on github READMEs
htmltools::HTML(glue("<div style = '{inline_style}'>Hello #RStats</div>"))
```


#### Inline styles - Example 2

Update the pervious style. Use the `prop` helper which uses autocomplete to help
build a standard property/value pair.

```{r}
inline_style$
  update(css_prop$`font-family`$monospace)$
  update(width = "25%", imp(color = 'green'), font_size = "25px")

inline_style
```


```{r echo = TRUE, eval = FALSE}
glue("<div style = '{inline_style}'>Hello #RStats</div>")
```

```{r echo = FALSE, eval = TRUE}
# Inline styles don't show up on github READMEs
htmltools::HTML(glue("<div style = '{inline_style}'>Hello #RStats</div>"))
```



# CSS Styles

CSS styles are identical to inline styles, except they must include a *selector* - 
this may be either a character string or a `Selector` object.

The selector can either be defined explicitly with a `selector = "greg"` argument, 
of if there is a single unnamed argument, that is assumed to be the selector.

```{r}
# Build a selector first
selector <- css_sel(".marsha")$child_of('carol')

# Build a style using this selector
style <- css_style(selector, colour = 'white')$
  update(css_prop$`text-align`$center)

style
```

```{r}
# Or simply use a character string for the selector
(css_style(".greg", colour = 'blue', margin = 'auto'))
```
